Stack Safety as a Security Property

### 2020-07-07 main.tex
queries in 2

    \row{\jal ~ \rra ~ 20}{??}{\PCname \leftarrow 20; ~ \rra \leftarrow \thepcctr}

@@

@@

\bcp{We should also emphasize, again, that there is no heap (if there were,
we might put it above the stack or between the instructions and the stack)}
First of all, we ignore the heap. We are mainly concerned
with stack interactions so that will be the main focus. \leo{We're
  going to come back to that at the end. Will we?} We also
abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated output at location 99, and lay the stack from
location 100 upwards. \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the memory layout at that point can be found in the top of
\cref{fig:running-trace-b}: instructions for {\tt main} begin at
0, the dedicated output is empty, while the (uninitialized) stack
begins at 100. Directly below the layout, we summarize the parts of
the register file that are relevant to the example.
%
The rest of \cref{fig:running-trace-b} details the execution of the
program, showing the machine state at call and return points, as well
as describing the full effect of each instruction in detail.
\leo{Expand upon this?}

>>>>

    \row{\jal ~ \rra ~ 20}{\rra \leftarrow \PCname + 1; ~ \PCname \leftarrow 20}{\rra \leftarrow \thepcctr; ~ \PCname \leftarrow 20}

@@

  \apt{How's that description for last line?}
  \apt{Where did these RISC-V insruction formats come from? I think some of them are just wrong, e.g.
    $\jal$ takes a PC-relative argument, not an absolute one, and the proper way to code a return to $\rra$ is $\jalr  ~ \rra ~ r_0$.
  But also the instruction operand ordering is awkward. Why not use standard AT\&T syntax?}

@@

\bcp{We should also emphasize, again, that there is no heap (if there were,
we might put it above the stack or between the instructions and the stack)}
First of all, we ignore the heap. We are mainly concerned
with stack interactions so that will be the main focus. \leo{We're
  going to come back to that at the end. Will we?} We also
abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated output at location 99, and lay the stack from
location 100 upwards. \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the memory layout at that point can be found in the top of
\cref{fig:running-trace-b}: instructions for {\tt main} begin at
0, the dedicated output is empty\apt{what does that mean? why not just uninitialized?}, while the (uninitialized) stack
begins at 100. Directly below the layout, we summarize the parts of
the register file that are relevant to the example.
%
The rest of \cref{fig:running-trace-b} details the execution of the
program, showing the machine state at call and return points, as well
as describing the full effect of each instruction in detail.
\leo{Expand upon this?}
